---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

## get_outputs = function(manifest) {
##   files = sapply(manifest, function(x) x$file)
##   comments = sapply(manifest, function(x) x$comment)
##   sizes = file.size(dest_files)
##   url=sprintf('<a href="%s">%s</a>', dest_files, files)
##   table = cbind(files, comments, sizes, url)
##   table
## }

manifest_df = copy_manifest_files(root, manifest,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
xt = xtable(manifest_df[, c("output", "comment", "size")],
            digits=0,
            caption="Summary of output files generated")
print(xt, include.rownames=FALSE, comment=FALSE)
```


# DRAFT

WARNING: this is work in progress, please do not cite or redistribute.

## To check

1. Are you happy with everything public on the github repo:  

2. I plan to put this work under MIT / CC0 licence for code and data.
   You are welcome to take the batch.sh files if they are useful to you.

3. Are you intending to share the two spreadsheets storing your pivot
   tables and two results?  Are you okay for me to share my two
   versions (not yet uploaded, but contain same results)?
   
4. Table A1 (my Figure C2) -- the numbers are roughly the same, but the
   colours are the wrong way round (red --> green).
   
5. Are you happy with the summary below?
   
# Summary

Given the large size of each simulation, and the number of
simulations, this took significant time (about 24 hours on a
departmental HPC server) to reproduce all the findings.  Simulations
were repeated using the public CovidSim implementation that was
released in May 2020 onto Github rather than the private code used to
generate the initial findings.  Small variations in the numbers were
detected between Report 9 and our runs which are due to several
factors:

1. The CovidSim codebase is now deterministic.
2. Slightly different population input files have been used.
3. Slight variations in the implementation of certain mitigiation
   strategies.

However, although the absolute values do not match the initial report,
the overall trends are consistent with the original report.  Note also
that my independent run matches runs by the Imperial team as of May
28th 2020.

\clearpage

# CODECHECKER notes

## Installation of CovidSim

The public version of CovidSim was cloned from
<https://github.com/mrc-ide/covid-sim>.  For these runs, the master
version from commit b12530 (27 May 2020) was used.  This version is
deterministic cross platform.  This was compiled for local
workstations and for a departmental HPC resource.


## Input parameter files

Input parameter files were provided by Prof Ferguson and are now
available at XXXX.

## Running the model

Powershell scripts to generate the Suppression and Mitigation results
were converted to bash and are provided in the codecheck repo.  These
bash scripts generate a list of jobs that can then be executed on a
local machine or submitted as jobs to a cluster.  More details below.

### Initialisation steps

In each of the Suppression and Mitigation folders, the output from
`runonce.sh` was run to generate two further input files,
*NetworkGB_8T.bin* and *NoInt_R0=2.4.avNE.severity.xls.* These files
were identical in the two folders.

Two folders were then generated to store the results of the batch runs

```
mkdir GB_suppress_release/mean8
mkdir GB_mitigation_release/MeanT8_NR10a
```

### Batch jobs

The list of jobs to run for each scenario was generated from the bash
scripts
[GB_suppress_release/batch.sh](https://github.com/codecheckers/covid-report9/blob/master/GB_suppress_release/batch.sh)
and
[GB_mitigation_release/batch.sh](https://github.com/codecheckers/covid-report9/tree/master/GB_mitigation_release).  These generated two job lists: 
[GB_suppress_release/batch-jobs.txt](https://github.com/codecheckers/covid-report9/blob/master/GB_suppress_release/batch-jobs.txt)
and
[GB_mitigation_release/batch-jobs.txt](https://github.com/codecheckers/covid-report9/blob/master/GB_mitigation_release/batch-jobs.txt)

These jobs were then run, and on a high-performance workstaion took
about 3 days, and about 1 day on our departmental HPC cluster.

### Analysis

Each run generated a CSV (labelled as an .xls) file in the output
folder.  An R script provided by Prof Ferguson was used to summarise
these runs into two summary files: [*stats_contain.csv*](<https://github.com/codecheckers/covid-report9/blob/master/GB_suppress_release/mean8/stats_contain.csv>)
and [*stats_mitigation.csv*](https://github.com/codecheckers/covid-report9/blob/master/GB_mitigation_release/MeanT8_NR10/stats_mitigation.csv).

These files were compared against the values generated by Prof
Ferguson and stored in the Excel spreadhseets using an R script.
These were found to be identical.  Inserting my results into his Excel
spreadsheet generated the same pivot tables.  I took screenshots of
these pivot tables to include for this report.


## Acknowledgements

I would like to thank Prof Ferguson and colleagues for promptly
answering any queries I had with this reproduction.  Dr Kacper Kornet
at the Faculty of Mathematics, University of Cambridge helped with
installation of CovidSim and job submission scripts for the HPC
cluster.  CODECHECK is financially supported by the Mozilla
foundation.

\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:4,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[3, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[4, "dest"])
cat('\n\n')
```

\clearpage
# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
